An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-30 uai2017/paper.tex
fix organization
update with 10 runs of gaussian mixture model experiment results

We have derived an M-H test for minibatch MCMC which approximates full data
tests. We present theoretical results and experimentally show the benefits of
our test on Gaussian mixtures and a variety of logistic regression experiments.

@@

\begin{table}[t]
\caption{Gaussian Mixture Model Statistics}
\small
\label{tab:poissons}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Metric/Method} & {\sc MHminibatch} & {\sc AustereMH(c)} & {\sc MHSubLhd} \\
\hline
\T Equation~\ref{eq:log_prob_poissons} & $-1306.2 \pm 20.7$ & $-1619.6 \pm 25.3$ & $-1301.5 \pm 44.4$ \\
Chi-Squared & $5706.8 \pm 2271.5$ & $ 10501.3 \pm 2076.5$ & $ 3711.7 \pm 1182.4$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

>>>>

We have derived an M-H test for minibatch MCMC which approximates full data
tests. We present theoretical results and experimentally show the benefits of
our test on Gaussian mixtures and a logistic regression experiment.

@@

\begin{table}[t]
\caption{Gaussian Mixture Model Statistics}
\small
\label{tab:poissons}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Metric/Method} & {\sc MHminibatch} & {\sc AustereMH(c)} & {\sc MHSubLhd} \\
\hline
\T Equation~\ref{eq:log_prob_poissons} & $-1307.0 \pm 229.5$ & $-1386.9 \pm 322.4$ & $-1295.1 \pm 278.0$ \\
Chi-Squared & $4502.3 \pm 1821.8$ & $ 5216.9 \pm 3315.8$ & $ 3462.3 \pm 1519.5$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}
